An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-29 EconGrowth.Rnw
Minor changes. But, did note that the bibliography is probably OK.

% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.

@@

\item{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references.}

@@

@@

To account for all energy input to an economy, we summed consumption data for many energy sources, including coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, and hydro). In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power were also included. Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011. For all other countries, we generated energy data for 1991--2011. Details on each of the energy quantifications are given in subsections below.

@@

\noindent The value of $E_{m,workers}$ was taken from a time series of kcal/day-person for workers in the U.S. from 1980--2011 \citep{Warr:2012a}. $E_{m,workers}$ is relatively constant over the period 1980--2011 at about ****** What is the value? *******, and the U.S. time series was assumed to apply to all economies.\footnote{The assumption that U.S. per-worker food intake applies to all economies introduces minor errors in human muscle work estimates for the various economies. However, human muscle work is never more than ****** \% of total energy consumption for any of the economies in this study, and we estimate that the error caused by this assumption is always less than ***** \% of total energy consumption for all economies.} The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.

>>>>

% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
\newcommand{\citeapos}[1]{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.

@@

@@

\item{\st{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references. I think the bibliography is OK.}}

@@

To account for all energy input to an economy, we summed consumption data for many energy sources, including coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, and hydro). In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power were also included. Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011 (except for useful work which is limited to the years 1980--2000 **** is this date range correct? ****). For all other countries, we generated energy data for 1991--2011. Details on each of the energy quantifications are given in subsections below.

@@

\noindent The value of $E_{m,workers}$ was taken from a time series of kcal/day-person for workers in the U.S. from 1980--2011 ***** Should this be 1980--2000 ??? ******  \citep{Warr:2012a}. $E_{m,workers}$ is relatively constant over the period 1980--2011 ***** Should this be 1980--2000 ???? **** at about ****** What is the value? *******, and the U.S. time series was assumed to apply to all economies.\footnote{The assumption that U.S. per-worker food intake applies to all economies introduces minor errors in human muscle work estimates for the various economies. However, human muscle work is never more than ****** \% of total energy consumption for any of the economies in this study, and we estimate that the error caused by this assumption is always less than ***** \% of total energy consumption for all economies.} The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.
